NumPy---Array Computation for Python

### 2019-12-17 paper.tex
Update outline
Add NEP 29 paragraph

NumFOCUS received a grant for \$195,000 in 2019 for the development of NumPy
and OpenBLAS from the Chan Zuckerberg Initiative. 
Ralf Gommers, the Director of Quansight Labs and a member of
the NumPy steering committee, is the PI.

@@

@@

\subsection*{Project goals / scope of library}

@@

@@

% \subsubsection*{Future Development}

\section*{Data Availability}
% The statement should be provided as a separate section (titled 'Data Availability') at the end of the main text, before the 'References' section.

>>>>

NumFOCUS received a grant for \$195,000 in 2019 for the development of NumPy
and OpenBLAS from the Chan Zuckerberg Initiative. 
NumPy depends on OpenBLAS to provide its underlying accelerated linear algebra implementation.
Ralf Gommers, the Director of Quansight Labs and a member of
the NumPy steering committee, is the PI.

@@

\subsubsection*{Project goals / scope of library}

\subsubsection*{NEPS revived and roadmap}

@@

@@

% https://numpy.org/neps/nep-0029-deprecation_policy.html
In NEP 29, we recommend, along with leaders from various other
projects, that all projects across the Scientific Python ecosystem
adopt a common ``time window-based'' policy for support of Python and
NumPy versions. This standard will simplify downstream project and
release planning.

@@

\subsubsection*{Future Development}

% Dtypes

We are busy overhauling the datatype system to make it consistent (aligned with
expectations), to simplify the creation of custom dtypes, and to enable much
requested features such as units.  The new implementation should be simpler and
more cleanly implemented.

A \href{https://github.com/numpy/numpy/pull/14422}{draft of DTypes NEP}
is under development in consultation with the community.

\section*{Data Availability}
